\begin{biblio}
    \bibitem{Bellman}
    Bellman, R.  The Dawn of Dynamic Programming / R. Bellman. -- Dover Publications. -- 2003.

    \bibitem{Pontryagin}
    Hazewinkel, M. Pontryagin maximum principle. Encyclopedia of Mathematics / M. Hazewinkel // Springer Science + Business Media B.V. -- 2001.

    \bibitem{Hogan}
    Hogan, W. M. Point-to-set maps in mathematical programming / W. M. Hogan // SIAM Review. -- 1973. -- Vol. 15, ¹3. -- P. 591-603.

    \bibitem{GalNedoma}
    Gal, T. Multiparametric linear programming / T. Gal, J. Nedoma // Management Science. -- 1972. -- P.406-442.

    \bibitem{Bemporad25}
    Bemporad A. The explicit linear quadratic regulator for constrained systems / A. Bemporad, M. Morari, V. Dua, and E.N. Pistikopoulos // Automatica. -- 2002. -- Vol. 38, ¹ 1. -- P. 3–20.

    \bibitem{GassSaaty}
    Gal. T. Parametric Programming /T. Gal. // de Gruyter. -- Berlin, 1995.
    
    \bibitem{Berkelaar28}
    Berkelaar A.B. The optimal set and optimal partition approach to linear and quadratic programming / A.B. Berkelaar, K. Roos, and T. Terlaky // Advances in Sensitivity Analysis and Parametric Programming /  T. Gal and H.J. Greenberg editors. -- 1997. -- CH. 6.
    
    \bibitem{Adler2}
    Adler I. I. A geometric view of parametric linear programming / Adler and R.D.C. Monteiro // Algorithmica. -- 1992. -- Vol. 8, ¹2. -- P. 161–176.
    
    \bibitem{Filippi}
    Filippi C. On the geometry of optimal partition sets in multiparametric linear programming / C. Filippi. // Department of Pure and Applied Mathematics, University of Padova. -- Italy, 1997.
    
    \bibitem{Dua57}
    Dua V. An algorithm for the solution of multiparametric mixed integer linear programming problems / V. Dua and E.N. Pistikopoulos. 
    
    \bibitem{Bemporad}
    Bemporad A. The explicit linear quadratic regulator for constrained systems / A. Bemporad, M. Morari, V. Dua, and E.N. Pistikopoulos // Automatica. -- 2002. -- Vol. 38, ¹1. -- P 3–20.
    
    \bibitem{ChenAllgower}
    Chen H. A Quasi-Infinite Horizon Nonlinear Model Predictive Control Scheme with Guaranteed Stability / H. Chen, F. Allgower // Automatica. -- 1998.

    \bibitem{Borelli}
    Borelli, F. Constrained Optimal Control of Linear and Hybrid Systems / F. Borelli // Lecture Notes in Control and Information Sciences. - Springer, 2003. - Vol. 290. - 293 p.
\end{biblio} 